---
title: "exam_simulation"
output: html_document
date: "2025-06-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 🔹 **Question 1: Control Flow, Loops, and Atomic Vectors**

You are given a numeric vector:

`nums <- c(12, 7, 5, 16, 8, 0, 23)`

**Tasks:**

a)  Write a `for` loop that prints whether each element is **positive**, **negative**, or **zero**.

    ```{r}
    nums <- c(12, 7, 5, 16, 8, 0, 23)
    for (i in nums) {
      if (i > 0){
        cat(i, "is positive \n")
        } else if(i < 0){
           cat(i, "is negative \n")
        } else cat(i, "is zero \n")


      }


    ```

b)  Use a `while` loop to print only the numbers in the vector that are **greater than 10**.

```{r}
j = 1
while(j < length(nums)){
  if(nums[j] > 10){
    cat(nums[j], "\n")
  }
  j = j + 1
}

```

a)  Count how many elements in `nums` are even numbers using a `for` loop and `if` statement.

```{r}
count = 0
for(i in nums){
    if(i %% 2 == 0){
      count = count + 1
    }
}
print(count)

```

------------------------------------------------------------------------

### 🔹 **Question 2: Matrices and Functions**

**Tasks:**

a)  Create a 4x4 matrix with values from 1 to 16, filled by row.\

```{r}
mat <- matrix(1:16, 4, 4)

```

a)  Write a function `above_threshold()` that takes a matrix and a threshold value as arguments and returns a **logical matrix** of the same size indicating which elements are greater than the threshold.

```{r}
logic = matrix(, nrow = 4, ncol = 4)
above_threshold <- function(threshold = 0) {
  return(mat > threshold)
}


```

a)  

b)  Use this function to find which elements in the matrix are greater than 10.

```{r}
print(above_threshold(12))

```

------------------------------------------------------------------------

### 🔹 **Question 3: Lists and Nested Access**

You are given the following list:

`book <- list(   title = "R for Beginners",   author = "Jane Doe",   year = 2021,   ratings = list(good = 15, average = 5, poor = 2) )`

```{r}
book <- list(   title = "R for Beginners",   author = "Jane Doe",   year = 2021,   ratings = list(good = 15, average = 5, poor = 2) )
book[[1]]
```

**Tasks:**

a)  Extract the title from the list.\

Extract the number of "average" ratings using double bracket `[[` notation.

```{r}
book[["ratings"]][["average"]]
```

\

Add a new element to the list called `publisher` with the value `"DataPress"`.

```{r}
book$Publisher = "DataPress" 
```

a)  Write a line of code that returns the sum of all ratings.

```{r}
sum(unlist(book[["ratings"]]))

```

------------------------------------------------------------------------

### 🔹 **Question 4: Data Frames and Apply Functions**

You have the following data frame:

`grades <- data.frame(   student = c("Alice", "Bob", "Charlie"),   math = c(90, 75, 85),   science = c(88, 80, 89),   english = c(92, 70, 85) )`

**Tasks:**

a)  Add a new column `average` containing the average of the three subjects for each student using `apply()`.

```{r}
grades <- data.frame(   student = c("Alice", "Bob", "Charlie"),   math = c(90, 75, 85),   science = c(88, 80, 89),   english = c(92, 70, 85) )
grades$average = apply(grades[, 2:4], 1, mean)
grades
?apply
```

a)  Add a `grade` column where:

    a)  "A" for average ≥ 90

    b)  "B" for average ≥ 80 and \< 90

    c)  "C" for average \< 80

(Hint: use `ifelse()` or `cut()`.)

```{r}
grades$grade = ifelse(grades$average >= 90, "A", ifelse(grades$average >= 80, "B", "C"))
grades
```

\

c)  Filter and return only students with a grade of "A".

```{r}
A_students = grades[grades$grade == "A",]
A_students

```

```{r}
print("Te amo Lizhen Shi")
```
